Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-02-13 hpmoon-asoco.tex
Mentioning the research gaps in conclusion for issue #32

%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
%ZDT1 
\textcolor{blue}{After establishing the performance of the new method and in order to
have some insight on how they work, let's check the effect of the different chromosome sizes and number of
islands. Plotting the solution sets allows to observe its quality, distribution and shape, specially if they are limited to 2 or 3 objectives, as in this paper \cite{Li17read}. } Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
final PFs of one arbitrary sample run of each combination;. The first
one, ZDT1, has a convex Pareto-optimal front. Comparing results from
$L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure
\ref{fig:plot_zdt1_2048}) it is apparent that the quality of the
generated PFs depends on the chromosome size. Specifically, all
configurations  with
$L=512$  seem to have a worse Spread and HV, on the other hand, the
SLA methods behave worse than $B$, as it was also shown on average in
Table \ref{tab:results512}. Nevertheless, if we focus on the plots
obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this
difference is less clear. Figure \ref{fig:plot_zdt1_2048} shows that
solutions obtained by the SLA methods show higher dispersion than the
baseline as $P$ grows. However, with $A$, the area covered by the PF
is still larger.

@@

Obtained results also show that when increasing the number of islands, the
automatic overlapping method ($A$) significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in automatic overlapping
methods, and not only the number of islands. Studying this factor with
more types of problems, and new configurations of population size and
chromosome lengths could be addressed in the future. Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested. But as we are dealing with complete individuals in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
For example, comparing 
different ways to calculate $c$ using linear, logarithmic or exponential functions
depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}. Moreover, a diversity analysis of the individuals
in each island during the algorithm run could be carried out to understand its influence
on the results. \textcolor{blue}{Parallel coordinates will be used when dealing with problems with more than 2 objectives \cite{Li17read}}.

@@

Also, more distributed implementations in several systems (such as a
GPUs or heterogeneous clusters) with different amounts of
islands/processors, could be used to perform a scalability study of the
different methods, being the transmission time between islands a
relevant issue to be addressed. \textcolor{blue}{Other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared. Moreover, new benchmarks and real problems
could be  used to validate this approach.}

>>>>

%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
%ZDT1 
\textcolor{blue}{After establishing the performance of the new method and in order to
have some insight on how they work, the effect of the different chromosome sizes and number of
islands can be checked. Plotting the solution sets allows to observe its quality, distribution and shape, specially if they are limited to 2 or 3 objectives, as in this paper \cite{Li17read}. } Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
final PFs of one arbitrary sample run of each combination;. The first
one, ZDT1, has a convex Pareto-optimal front. Comparing results from
$L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure
\ref{fig:plot_zdt1_2048}) it is apparent that the quality of the
generated PFs depends on the chromosome size. Specifically, all
configurations  with
$L=512$  seem to have a worse Spread and HV, on the other hand, the
SLA methods behave worse than $B$, as it was also shown on average in
Table \ref{tab:results512}. Nevertheless, if we focus on the plots
obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this
difference is less clear. Figure \ref{fig:plot_zdt1_2048} shows that
solutions obtained by the SLA methods show higher dispersion than the
baseline as $P$ grows. However, with $A$, the area covered by the PF
is still larger.

@@

Obtained results also show that when increasing the number of islands, the
automatic overlapping method ($A$) significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in automatic overlapping
methods, and not only the number of islands. 
%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
Since our method divides the individuals into blocks of divisible size, aggregation methods after migration, such as the ones used in \cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be also tested. But as we are dealing with complete individuals in each island, the possibility of using a real number, such as 0.3 (30\% overlapping) instead an integer value opens future experimental setups.
For example, comparing 
different ways to calculate $c$ using linear, logarithmic or exponential functions
depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}.

\textcolor{blue}{Although the results obtained in this work are promising, it is clear that this method requires more future experiments, in addition to the automatic calculation of $c$. These new experiments should involve a more complete parameter study, including a sensitivity analysis, to validate our approach. Other benchmarks and real problems should be addressed in the future. These problems could involve dealing with more than two objectives, so polar coordinates should be used to visually understand the results \cite{Li17read}. Also, other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared.}

% Moreover, a diversity analysis of the individuals in each island during the algorithm run could be carried out to understand its influence on the results.

@@

Finally, more distributed implementations in several systems (such as a
GPUs or heterogeneous clusters) with different amounts of
islands/processors, could be used to perform a scalability study of the
different methods, being the transmission time between islands a
relevant issue to be addressed.
